### 2024-06-11 paper/tex/06-extensions.tex
corrections

\paragraph{Solution 1: Declarative Normalization}
One way to resolve this ambiguity is to fix the order of quantifiers.  
The algorithm already performs the ordering of the quantifiers in the normalization procedure.
This way, we could require the inferred type to be normalized
to specify the order of the quantifiers:
$$\ottdruleDTTypeAppOrderedLabeled{}$$

@@

\paragraph{Solution 2: Elementary Type Inference}
An alternative approach to provide explicit type application
 was proposed by \cite{zhao22:elementary}.
In this work, the subtyping relation is restricted 
in such a way that 
$[[∀α⁺.∀β⁺.iN]]$ and $[[∀β⁺.∀α⁺.iN]]$ are \emph{not} mutual subtypes 
(as long as $[[α⁺ ∊ fv(iN)]]$ and $[[β⁺ ∊ fv(iN)]]$).
It implies that the order of the quantifiers of the inferred type is unique,
and thus, the explicit type application is unambiguous.

@@

\paragraph{Solution 3: labeled quantifiers}

@@

\paragraph{The Algorithm}

@@

    For brevity, we omit the details of the bidirectional algorithm.
    Let us discuss one especially important rule---arrow application inference. 
    An intuitive way to bidirectionalize this rule is the following:
    $$ \ottdruleATArrowAppBidirLabeled{} $$
    % \paragraph{Reaching Undecidability}
    However, this rule is too permissive. 
    The judgement $[[Γ ; Φ ⊨ v ⇐ uQ ⫤ SC1]]$
    requires us to check a term against an \emph{algorithmic} 
    type $[[uQ]]$. Further, through the
    lambda function checking \ruleref{\ottdruleDTtLamChkLabel}
    the algorithmic types infiltrate the type context
    and then through variable inference and subsumption, 
    \emph{both} sides of subtyping. 
    This way, \ruleref{\ottdruleATArrowAppBidirLabel}
    compromises the important invariant
    of the subtyping algorithm: 
    now the same algorithmic variable can occur on \emph{both}
     sides of the subtyping relation.

@@

    % \paragraph{Restricting Inference}
    Instead, we strengthen
    \ruleref{\ottdruleATArrowAppBidirLabel}
    in such a way that it never checks a term against an algorithmic type.
    Instead, type checking $[[v]]$ against $[[uQ]]$ is replaced by 
    a more restrictive premise---checking that $[[v]]$ \emph{synthesizes a subtype} of $[[uQ]]$:
    $$ \ottdruleATArrowAppBidirSLabeled{} $$\\

>>>>

\paragraph*{Solution 1: Declarative Normalization}
One way to resolve this ambiguity is to fix the order of quantifiers.  
The algorithm already performs the ordering of the quantifiers in the normalization procedure.
This way, we could require the inferred type to be normalized
to specify the order of the quantifiers:
$$\ottdruleDTTypeAppOrderedLabeled{}$$

@@

\paragraph*{Solution 2: Elementary Type Inference}
An alternative approach to provide explicit type application
 was proposed by \cite{zhao22:elementary}.
In this work, the subtyping relation is restricted 
in such a way that 
$[[∀α⁺.∀β⁺.iN]]$ and $[[∀β⁺.∀α⁺.iN]]$ are \emph{not} mutual subtypes 
(as long as $[[α⁺ ∊ fv(iN)]]$ and $[[β⁺ ∊ fv(iN)]]$).
It implies that the order of the quantifiers of the inferred type is unique,
and thus, the explicit type application is unambiguous.

@@

\paragraph*{Solution 3: labeled quantifiers}

@@

\paragraph*{The Algorithm}

@@

    For brevity, we omit the details of the bidirectional algorithm.
    Let us discuss one especially important rule---arrow application inference. 
    An intuitive way to bidirectionalize this rule is the following:
    $$ \ottdruleATArrowAppBidirLabeled{} $$
    % \paragraph*{Reaching Undecidability}
    However, this rule is too permissive. 
    The judgement $[[Γ ; Φ ⊨ v ⇐ uQ ⫤ SC1]]$
    requires us to check a term against an \emph{algorithmic} 
    type $[[uQ]]$. Further, through the
    lambda function checking \ruleref{\ottdruleDTtLamChkLabel}
    the algorithmic types infiltrate the type context
    and then through variable inference and subsumption, 
    \emph{both} sides of subtyping. 
    This way, \ruleref{\ottdruleATArrowAppBidirLabel}
    compromises the important invariant
    of the subtyping algorithm: 
    now the same algorithmic variable can occur on \emph{both}
     sides of the subtyping relation.

@@

    % \paragraph*{Restricting Inference}
    Instead, we strengthen
    \ruleref{\ottdruleATArrowAppBidirLabel}
    in such a way that it never checks a term against an algorithmic type.
    Instead, type checking $[[v]]$ against $[[uQ]]$ is replaced by 
    a more restrictive premise---checking that $[[v]]$ \emph{synthesizes a subtype} of $[[uQ]]$:
    $$ \ottdruleATArrowAppBidirSLabeled{} $$\\
